%-----------EXPERIENCE-----------%
\section{Experience}\label{sec:experience}
\startListPointOneInchAwayFromLeft

\resumeSubheadingExperience{Amazon India}{Software Development Engineer II}{Oct 2021 -- Present}

\resumeItemListStart
\resumeItemMiniPage{Grew Prime stacking sign-ups to 4× (500 → 2,000/day) by \textbf{launching Stacking CX on high-traffic surfaces} (Home page, Order Thank-You page, Whatsapp) targeted to users near plan expiry;  $\sim620K$ incremental customers/year and $\sim6M$ annual impact in revenue.}
\resumeItemMiniPage{Designed and built a generic \textbf{prime lifecycle event scheduler} for cross-channel upsell (live for Prime homepage upsell \& WhatsApp), orchestrating $\sim150K$ notifications/day and driving $\sim1.2-1.5K$ Prime sign-ups from scheduled surfaces.}
\resumeItemMiniPage{Owned the \textbf{infrastructure migration} of Retention Notification AWS Lambda service from eu-west-1 to eu-south-2 as part of on-going WW initiative to reduce load to eu-west-1 region on a 3-week deadline.}
\resumeItemMiniPage{Enabled device-based \textbf{card tokenisation for INPrime} to meet the RBI mandate, which involved \textbf{redesigning the plan buying journey} for new users and \textbf{rescuing ~4–5 million existing customers} by collaborating with BillDesk and the cards team to complete the tokenisation.}
\resumeItemMiniPage{Drove a $\sim3\%$ improvement in subscription payment success by launching a \textbf{recurring charge monitoring dashboards} that provided critical failure insights and enabled targeted fixes with partner teams.}
\resumeItemMiniPage{Led the architecture and implementation of Prime's mandatory migration from legacy Standing Instruction to \textbf{E-Mandate based recurring charge.} This involved orchestrating various lifecycle events (e.g. mandate setup, pause, deletion) resulting in regulatory compliance, enhanced user experience and a notable \textbf{$\sim4\%$ uplift in recurring payment success rates}.}
\resumeItemMiniPage{Launched a \textbf{Revise Payment CX} for members whose renewals fail for retriable reasons (e.g. insufficient funds). During the post-expiry grace window, customers can update their payment method for auto-retry, preventing $\sim20K$ annual churn.}
\resumeItemMiniPage{Launched \textbf{Auto-Renew Enable Customer Experience (CX)} on high-traffic surfaces (Home and Retail Thank-You pages), significantly lowering involuntary churn and \textbf{retaining an estimated $\sim30-40K$ members annually}.}
\resumeItemListEnd

\resumeSubheadingExperience{Goldman Sachs}{Technology Analyst}{Jul 2019 -- Oct 2021}
\resumeItemListStart
\resumeItem{Led end-to-end integration of SAP Concur(https://www.concur.co.in/) with Goldman Sachs reimbursement system, including building a Spring Batch–based processing adapter for merchant without native integration with Concur.}
\resumeItem{Implemented core modules for Goldman Sachs’ Electronic Trading (GSET) platform as it transitioned from C++ to a GC-free Java stack, delivering ~X\% faster execution on my components and shortening release cycles.}
\resumeItemListEnd

\resumeSubheadingExperience{Samsung R\&D Center}{Software Development Intern}{Jan 2019 -- June 2019}
\resumeItemListStart
\resumeItem{Implemented remote monitoring and control for IoT-enabled doors in Samsung SmartThings, achieving \textgreater80\% test coverage using AngularJS, ExpressJS, Mocha, Mongoose, and Node.js.}
\resumeItemListEnd

\makeLinePointOneInchAwayEnd